Effect of Election on Currency Fluctuation

### 2024-04-16 paper/paper.qmd
newst rendering of paper.pdf, with updated fig-size_visual

exchange_inaug |>
  ggplot(aes(
    x = date,
    y = exchange_rate
  )) +
  geom_point(alpha = 0.005) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 0),
    method = "lm",
    aes(color = "No Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1974-08-06" & date <= "1974-08-12"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1977-01-17" & date <= "1977-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1981-01-17" & date <= "1981-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1981-01-17" & date <= "1981-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1989-01-17" & date <= "1989-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1993-01-17" & date <= "1993-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2001-01-17" & date <= "2001-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2009-01-17" & date <= "2009-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2017-01-17" & date <= "2017-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2021-01-17" & date <= "2021-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) + scale_color_manual(values = colors) +
  labs(
    x = "Date",
    y = "USD v.s. CAD Exchange Rate",
    title = "Exchange Rate from 1974 to 2024",
    color = "Period"
  ) + theme(legend.position = "bottom")

>>>>

exchange_inaug |>
  ggplot(aes(
    x = date,
    y = exchange_rate
  )) +
  geom_line(alpha = 0.1) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 0),
    method = "lm",
    aes(color = "No Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1974-08-06" & date <= "1974-08-12"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1977-01-17" & date <= "1977-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1981-01-17" & date <= "1981-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1981-01-17" & date <= "1981-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1989-01-17" & date <= "1989-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1993-01-17" & date <= "1993-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2001-01-17" & date <= "2001-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2009-01-17" & date <= "2009-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2017-01-17" & date <= "2017-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2021-01-17" & date <= "2021-01-23"),
    method = "lm",
    aes(color = "Inauguration Announcement"),
    formula = "y ~ x"
  ) + scale_color_manual(values = colors) + theme_minimal() +
  labs(
    x = "Date",
    y = "USD v.s. CAD Exchange Rate",
    title = "Exchange Rate from 1974 to 2024",
    color = "Period"
  ) + theme(legend.position = "bottom")
